\vspace{-0.8in}Brief Announcement: A Family of Leaderless Generalized-Consensus Algorithms

### 2016-02-12 podc16/paper2.tex
no appendix
property references

\author{
Author 1\\
ECE, Virginia Tech\\
email
\and
Author 2\\
ECE, Virginia Tech\\
email
\and
Author 3\\
ECE, Virginia Tech\\
email
}

@@

\section{Introduction}

@@

\subsection{Satisfying Consistency and Liveness of Generalized Consensus}
Consider an execution of the algorithm.
\begin{mylemma}\label{lemma:compat}
If $g_p^1$ is the graph $g_p$ at time $t_1$, $g_q^2$ is the graph $g_q$ at time $t_2$, then $g_p^1$ and $g_q^2$ are compatible.
\end{mylemma}
\begin{proof*}
Follows from the safety property (b) of the map-agreement algorithm and definition of the graph $g_p$.
From (b) it follows that if $c$ is in the domain of both $m_p$ and $m_q$ then $m_p\left[ c \right] = m_q\left[ c \right]$.
\end{proof*}
\begin{mythm}
    The consistency property always holds.
    \label{lemma:consistency}
\end{mythm}
\begin{proof*}
    By \cref{lemma:compat} and the safety property (b) of the dependency-set algorithm, $g_p^1$ and $g_q^2$ satisfy the premises of \cref{lemma:graph}. Therefore we get that $g_p^1$ and $g_q^2$ are compatible.
\end{proof*}
\begin{mythm}
    If a command $c$ which is GC-proposed is then repeatedly GC-proposed, then a c-struct containing $c$ is eventually decided.
\end{mythm}
\begin{proof*}
    The liveness properties (a) and (b) of the dependency-set algorithm ensures that some dependency sets are repeatedly proposed for $c$ to the map-agreement algorithm, as long as a commit is not observed. Moreover, the map-agreement algorithm ensures that when dependency sets are repeatedly proposed for $c$, then a dependency set will eventually be committed for $c$. Similarly, any dependency of $c$ is eventually committed and $c$ becomes executable, at which points it is included in the next decided c-struct.
\end{proof*}

>>>>

\begin{comment}
\author{
{\small Author 1}\\
{\small ECE, Virginia Tech}\\
{\small email}
\and
{\small Author 2}\\
{\small ECE, Virginia Tech}\\
{\small email}
\and
{\small Author 3}\\
{\small ECE, Virginia Tech}\\
{\small email}
}
\end{comment}

%\begin{comment}

\author{
Giuliano Losa\\
ECE, Virginia Tech\\
giuli4no@vt.edu
\and
Sebastiano Peluso\\
ECE, Virginia Tech\\
peluso@vt.edu
\and
Binoy Ravindran\\
ECE, Virginia Tech\\
binoy@vt.edu
}
%\end{comment}

@@

\vspace{-0.5cm}
\section{Introduction}

@@

\subsection{Satisfying Consistency and Liveness of Generalized Consensus}
Consider an execution of the algorithm.
\begin{mylemma}\label{lemma:compat}
If $g_p^1$ is the graph $g_p$ at time $t_1$, $g_q^2$ is the graph $g_q$ at time $t_2$, then $g_p^1$ and $g_q^2$ are compatible.
\end{mylemma}
\begin{proof*}
TODO
%Follows from the safety property (b) of the map-agreement algorithm and definition of the graph $g_p$.
%From (b) it follows that if $c$ is in the domain of both $m_p$ and $m_q$ then $m_p\left[ c \right] = m_q\left[ c \right]$.
\end{proof*}
\begin{mythm}
    The consistency property of generalized consensus always holds.
    \label{lemma:consistency}
\end{mythm}
\begin{proof*}
    By \cref{lemma:compat} and \ref{suggestion-agreement}, $g_p^1$ and $g_q^2$ satisfy the premises of \cref{lemma:graph}. Therefore we get that $g_p^1$ and $g_q^2$ are compatible.
\end{proof*}
\begin{mythm}
    If a command $c$ which is GC-proposed is then repeatedly GC-proposed, then a c-struct containing $c$ is eventually decided.
\end{mythm}
\begin{proof*}
    The properties \ref{eventual-suggestion} and \ref{re-suggest} ensure that dependency sets are repeatedly proposed for $c$ to the map-agreement algorithm as long as a commit is not observed. Moreover, the map-agreement algorithm ensures that when dependency sets are repeatedly proposed for $c$, then a dependency set will eventually be committed for $c$. Similarly, any dependency of $c$ is eventually committed and $c$ becomes executable, at which points it is included in the next decided c-struct.
\end{proof*}
